Milestone 2: Datasets Generation

### 2021-11-04 perf_release_criteria/milestone_3/feature_selection/feature_selection_nn_gam_logit_f.Rmd

```{r data_load, echo=FALSE}
file_name = 'df_train_validate_20191021.RData'
image_file_path = file.path('data', file_name)

# Pull from GCP if necessary
# library(googleCloudStorageR)
# Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
#            "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
# gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)

@@

>>>>

```{r data_load, echo=FALSE, message=FALSE}
file_name = 'df_train_validate_20191025.RData'
image_file_path = file.path('data', file_name)

# Pull from GCP if necessary
if (!file.exists(image_file_path)){
  Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
  library(googleCloudStorageR)
  gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)
}

@@

# FS 1 Interactions

Feature selection on only performance metrics, but including interaction terms.

```{r fs1_int, error=TRUE}
res_fs1_int <- list()
for (bt in names(bts)){
  res_fs1_int[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, workers = 10, add_interactions=TRUE,
                                      replace=TRUE, distance = 'linear.logit')
}
save.image(results_file_path)
print(res_fs1_int)
```

```{r fs1_int_noreplace, error=TRUE}
res_fs1_int_noreplace <- list()
for (bt in names(bts)){
  res_fs1_int_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, add_interactions=TRUE,
                                                replace=FALSE, workers = 10, distance = 'linear.logit')
}
save.image(results_file_path)
print(res_fs1_int_noreplace)
```

### 2021-11-04 perf_release_criteria/milestone_3/feature_selection/feature_selection_nn_logit.Rmd

---
title: "Milestone 2: Feature Selection - Nearest Neighbors, GAM Logit"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_notebook:
    theme: cosmo
    toc: true
    toc_float: true
---

@@

**Matching Algorithm Tested**: Nearest-neighbors with GAM logit distance metric

@@

results_file_name <- 'feature_selection_nn_gam_logit.RData' 
results_file_path <- file.path('data', results_file_name)
```

@@

```{r fs1, error=TRUE}
res_fs1 <- list()
for (bt in names(bts)){
  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs1)
```

```{r fs1_noreplace, error=TRUE}
res_fs1_noreplace <- list()
for (bt in names(bts)){
  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs1_noreplace)
```

@@

```{r fs2, error=TRUE}
res_fs2 <- list()
for (bt in names(bts)){
  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs2)
```

```{r fs2_noreplace, error=TRUE}
res_fs2_noreplace <- list()
for (bt in names(bts)){
  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs2_noreplace)
```

@@

```{r fs3, error=TRUE}
res_fs3 <- list()
for (bt in names(bts)){
  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs3)
```

```{r fs3_noreplace, error=TRUE}
res_fs3_noreplace <- list()
for (bt in names(bts)){
  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs3_noreplace)
```

@@

```{r fs4, error=TRUE}
res_fs4 <- list()
for (bt in names(bts)){
  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs4)
```

```{r fs4_noreplace, error=TRUE}
res_fs4_noreplace <- list()
for (bt in names(bts)){
  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs4_noreplace)
```

@@

```{r fs5, error=TRUE}
res_fs5 <- list()
for (bt in names(bts)){
  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs5)
```

```{r fs5_noreplace, error=TRUE}
res_fs5_noreplace <- list()
for (bt in names(bts)){
  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs5_noreplace)
```

@@

```{r fs6, error=TRUE}
res_fs6 <- list()
for (bt in names(bts)){
  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs6)
```

```{r fs6_noreplace, error=TRUE}
res_fs6_noreplace <- list()
for (bt in names(bts)){
  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs6_noreplace)
```

@@

```{r fs7, error=TRUE}
res_fs7 <- list()
for (bt in names(bts)){
  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs7)
```

```{r fs7_noreplace, error=TRUE}
res_fs7_noreplace <- list()
for (bt in names(bts)){
  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs7_noreplace)
```

>>>>

---
title: "Milestone 2: Feature Selection - Nearest Neighbors, Logit"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_notebook:
    theme: cosmo
    toc: true
    toc_float: true
---

@@

**Matching Algorithm Tested**: Nearest-neighbors with logit distance metric

@@

results_file_name <- 'feature_selection_nn_logit.RData' 
results_file_path <- file.path('data', results_file_name)
```

@@

```{r fs1, error=TRUE}
res_fs1 <- list()
for (bt in names(bts)){
  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=TRUE, workers = 10, distance = 'logit')
}
save.image(results_file_path)
print(res_fs1)
```

```{r fs1_noreplace, error=TRUE}
res_fs1_noreplace <- list()
for (bt in names(bts)){
  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=FALSE, workers = 10, distance = 'logit')
}
save.image(results_file_path)
print(res_fs1_noreplace)
```

@@

```{r fs2, error=TRUE}
res_fs2 <- list()
for (bt in names(bts)){
  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=TRUE, workers = 10, distance = 'logit')
}
save.image(results_file_path)
print(res_fs2)
```

```{r fs2_noreplace, error=TRUE}
res_fs2_noreplace <- list()
for (bt in names(bts)){
  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=FALSE, workers = 10, distance = 'logit')
}
save.image(results_file_path)
print(res_fs2_noreplace)
```

@@

```{r fs3, error=TRUE}
res_fs3 <- list()
for (bt in names(bts)){
  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=TRUE, workers = 10, distance = 'logit')
}
save.image(results_file_path)
print(res_fs3)
```

```{r fs3_noreplace, error=TRUE}
res_fs3_noreplace <- list()
for (bt in names(bts)){
  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=FALSE, workers = 10, distance = 'logit')
}
save.image(results_file_path)
print(res_fs3_noreplace)
```

@@

```{r fs4, error=TRUE}
res_fs4 <- list()
for (bt in names(bts)){
  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=TRUE, workers = 10, distance = 'logit')
}
save.image(results_file_path)
print(res_fs4)
```

```{r fs4_noreplace, error=TRUE}
res_fs4_noreplace <- list()
for (bt in names(bts)){
  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=FALSE, workers = 10, distance = 'logit')
}
save.image(results_file_path)
print(res_fs4_noreplace)
```

@@

```{r fs5, error=TRUE}
res_fs5 <- list()
for (bt in names(bts)){
  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=TRUE, workers = 10, distance = 'logit')
}
save.image(results_file_path)
print(res_fs5)
```

```{r fs5_noreplace, error=TRUE}
res_fs5_noreplace <- list()
for (bt in names(bts)){
  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=FALSE, workers = 10, distance = 'logit')
}
save.image(results_file_path)
print(res_fs5_noreplace)
```

@@

```{r fs6, error=TRUE}
res_fs6 <- list()
for (bt in names(bts)){
  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=TRUE, workers = 10, distance = 'logit')
}
save.image(results_file_path)
print(res_fs6)
```

```{r fs6_noreplace, error=TRUE}
res_fs6_noreplace <- list()
for (bt in names(bts)){
  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=FALSE, workers = 10, distance = 'logit')
}
save.image(results_file_path)
print(res_fs6_noreplace)
```

@@

```{r fs7, error=TRUE}
res_fs7 <- list()
for (bt in names(bts)){
  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=TRUE, workers = 10, distance = 'logit')
}
save.image(results_file_path)
print(res_fs7)
```

```{r fs7_noreplace, error=TRUE}
res_fs7_noreplace <- list()
for (bt in names(bts)){
  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=FALSE, workers = 10, distance = 'logit')
}
save.image(results_file_path)
print(res_fs7_noreplace)
```

### 2021-11-04 perf_release_criteria/milestone_3/feature_selection/feature_selection_nn_logit_linear.Rmd

```{r fs2_int, error=TRUE}
res_fs2 <- list()
for (bt in names(bts)){
  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, add_interactions=TRUE,
                                      replace=TRUE, workers = 10, distance = 'linear.logit')
}
save.image(results_file_path)
print(res_fs2)
```

>>>>

```{r fs2_int, error=TRUE}
# res_fs2 <- list()
# for (bt in names(bts)){
#   res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, add_interactions=TRUE,
#                                       replace=TRUE, workers = 10, distance = 'linear.logit')
# }
# save.image(results_file_path)
# print(res_fs2)
```

### 2021-11-04 perf_release_criteria/milestone_3/hyperparameter_tuning/hyperparameter_tuning_nn_malahanobis.Rmd

# Pull from GCP if necessary
# library(googleCloudStorageR)
# Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
#            "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
# gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)

@@

To investigate, and possible utilize, a more general model, the second highest suite of features will also be tested:

* Beta oversapmling by 16x
* FS 3: Performance metrics and highest found by Boruta with equal labels dataset

@@

* Matching order (m.order)
* Caliper
* of control to treatments

@@

# FS 1
Hyperparameter tuning on optimal features.

@@

perform_matchit_hp_tune(df_train_f, bt[[1]], fs1, size=5000, workers = 10, hps_grid = hps_grid, distance = "mahalanobis")
```

>>>>

# Pull from GCP if necessary
if (!file.exists(image_file_path)){
  Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
  library(googleCloudStorageR)
  gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)

}
load(image_file_path)
```

@@

To investigate, and possible utilize, a more general model, two other suite of high scoring features will also be tested:

1. Contains performance metrics
    * Beta oversapmling by 16x
    * FS 3: Performance metrics and highest found by Boruta with equal labels dataset
2. No performance metrics: 
    * Beta oversapmling by 8x
    * FS 5: Highest found by Boruta

@@

* `replace`: Can each control unit be matched to more than one treated unit?
* `caliper`:  The number of standard deviations of the distance measure within which to draw control units.
* `calclosest`: Whether to take the nearest available match if no matches are available within the `caliper`.
* `ratio`: #  of control units to match to each test.

@@

# FS 1
## Coarse Grid
Hyperparameter tuning on optimal features.

@@

fs1_results <- perform_matchit_hp_tune(df_train_f, bt, fs1, size=NULL, workers = 64, hps_grid = hps_grid, distance = "mahalanobis")
save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)

fs1_results_df <- fs1_results %>% bind_rows()
fs1_results_df %>% group_by_at(setdiff(names(fs1_results_df), "scores")) %>% 
  summarise(mean = mean(scores), sd = sd(scores), median = median(scores)) -> fs1_results_df
knitr::kable(fs1_results_df[order(fs1_results_df$mean), ] %>% head(n=20))

```

## Fine Grid

```{r hp_fine}
hps_fine <- list(
  replace = c(FALSE),
  caliper = seq(0, 3, by=0.2),
  calclosest = c(TRUE, FALSE),
  ratio = c(1, 2)
)

hps_fine_grid = expand.grid(hps_fine)
```

```{r fs1_fine, error=TRUE}
hps_fine_grid = expand.grid(hps_fine)

fs1_results_final <- perform_matchit_hp_tune(df_train_f, bts[['bts_4x']], fs1, size=NULL, workers = 64, hps_grid = hps_fine_grid, 
                                       distance = "mahalanobis", add_interactions=FALSE)
save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)

fs1_results_df <- fs1_results_final %>% bind_rows()
fs1_results_df %>% group_by_at(setdiff(names(fs1_results_df), "scores")) %>% 
  summarise(mean = mean(scores), sd = sd(scores), median = median(scores)) -> fs1_results_df
knitr::kable(fs1_results_df[order(fs1_results_df$median), ] %>% head(20))
```

# FS 3

```{r fs3, error=TRUE}
fs3_results <- perform_matchit_hp_tune(df_train_f, bts[['bts_16x']], fs3, size=NULL, workers = 64, hps_grid = hps_grid, distance = "mahalanobis")
save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)

fs3_results_df <- fs3_results %>% bind_rows()
fs3_results_df %>% group_by_at(setdiff(names(fs3_results_df), "scores")) %>% 
  summarise(mean = mean(scores), sd = sd(scores), median = median(scores)) -> fs3_results_df
knitr::kable(fs3_results_df[order(fs3_results_df$median), ] %>% head(n=20))
```

# FS 5

```{r fs5, error=TRUE}
fs5_results <- perform_matchit_hp_tune(df_train_f, bts[['bts_8x']], fs5, size=NULL, workers = 64, hps_grid = hps_grid, distance = "mahalanobis")
save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)

fs5_results_df <- fs5_results %>% bind_rows()
fs5_results_df %>% group_by_at(setdiff(names(fs5_results_df), "scores")) %>% 
  summarise(mean = mean(scores), sd = sd(scores), median = median(scores)) -> fs5_results_df
knitr::kable(fs5_results_df[order(fs5_results_df$median), ])
```

# Push to GCP
Save the resultant dataset and bootstrap samples to an R image.

```{r gcp_storage_push, warning=FALSE}
gcs_file_path <- file.path('data', 'milestone2', results_file_name)

Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")

library(googleCloudStorageR)

upload_try <- gcs_upload(results_file_path, name = gcs_file_path)
upload_try
```

### 2021-11-04 perf_release_criteria/milestone_3/ms_2_dataset_generation.Rmd

df_train <- load_df('data/df_pd_67.csv')
df_validate <- load_df('data/df_pd_68.csv')
```

@@

The feature selection will utilize 10 boostrap replicates, which are generated as follows:
1. The entire `df_train` dataset is sampled at 100% with replacement.
2. A sample of Release (`is_release = TRUE`) `client_id` are taken of the same size as Beta (`r channel_counts$n[channel_counts$label == 'beta']`)
3. The entire (resampled) Beta `client_id` are combined with this sampled Release ids. 
    - These are the profiles that will be used for building the matching model. 
    - The matched Beta profiles will be used for scoring the model. 
4. The remaining Release ids will be used for scoring the model.

>>>>

df_train <- load_df('data/df_pd_67_20191026.csv')
df_validate <- load_df('data/df_pd_68_20191026.csv')
```

@@

The feature selection will utilize 10 boostrap replicates, which are generated as follows:

1. The entire `df_train` dataset is sampled at 100% with replacement.
2. A sample of Release (`is_release = TRUE`) `client_id` are taken of the same size as Beta (`r channel_counts$n[channel_counts$label == 'beta']`)
3. The entire (resampled) Beta `client_id` are combined with these sampled Release ids. 
    - These are the profiles that will be used for building the matching model. 
    - The matched Beta profiles will be used for scoring the model. 
4. The remaining Release ids will be used for scoring the model.
